ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
fixing typos on introduction
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
GPU verification \sep formal verification \sep model checking \sep CUDA

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

@@

A distinct feature of ESBMC-GPU, when compared with other approaches \cite{betts:2012,Li:2010,Li:2012,civl:2015}, is the use of Bounded Model Checking (BMC)~\cite{Biere:2009} allied to Satisfiability Modulo Theories (SMT)~\cite{Barrett:2009}, with explicit state-space exploration~\cite{cordeiro:2011,cordeiro:2012}. In summary, concurrency problems are tackled, up to an unwinding bound, while each interleaving itself is symbolically handled; however, even with BMC, space-state exploration may become a very time-consuming task, which is alleviated through state hashing and Monotonic Partial Order Reduction (MPOR)~\cite{KahlonWG09}. As a consequence, redundant interleavings are eliminated, without ignoring a program's behavior.

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}

@@

@@

@@

\begin{keyword}
GPU verification \sep formal verification \sep model checking \sep CUDA

@@

A distinct feature of ESBMC-GPU, when compared with other approaches \cite{betts:2012,Li:2010,Li:2012,civl:2015}, is the use of Bounded Model Checking (BMC)~\cite{Biere:2009} allied to Satisfiability Modulo Theories (SMT)~\cite{Barrett:2009}, with explicit state-space exploration~\cite{cordeiro:2011,cordeiro:2012}. In summary, concurrency problems are tackled, up to an unwinding bound, while each interleaving itself is symbolically handled; however, even with BMC, state-space exploration may become a very time-consuming task, which is alleviated through state hashing and Monotonic Partial Order Reduction (MPOR)~\cite{KahlonWG09}. As a consequence, redundant interleavings are eliminated, without ignoring a program's behavior.
